---
title: "Microstructure-descriptives"
author: "Bari Fuchs"
date: "8/6/2020"
output: word_document
editor_options: 
  chunk_output_type: console
---

This file is being updated following an OS upgrade to 10.15, which introduced issues with code

```{r data org, include=FALSE}
library(plyr)
library(dplyr)
library(readr)
library(hms)
#install.packages("chron")
library(chron)

#### import data ####
#basedir <- ("~/Box/0-Bari_files/00_PennState/Bout_Project")
basedir <- ("~/OneDrive - The Pennsylvania State University/Bari-files-Manual-Box-Transfer/00_PennState/Bout_Project")

setwd(file.path(basedir,"Data/Intervals/"))

#myfiles = list.files(pattern="*.csv", full.names=TRUE)
myfiles = list.files(pattern="*.csv")
list.files()
dat_csv = ldply(myfiles, read_csv)

#### set class of variables ####
dat_csv$IBI <- as.numeric(dat_csv$IBI)
dat_csv$InterEatInt_f <- as.numeric(dat_csv$InterEatInt_f)
dat_csv$InterEatInt_n <- as.numeric(dat_csv$InterEatInt_n)
dat_csv$chewtimes <- as.numeric(dat_csv$chewtimes)
dat_csv$id <- as.numeric(dat_csv$id)

#### Recode mis-coded variables ####
# Note: For AUR0076, "eat_f" is coded as "eat" ; "eat_n" is coded as "other chew"
unique(dat_csv$Annotation)
dat_csv$Annotation[dat_csv$Annotation == "eat"] <- "eat_f"
dat_csv$Annotation[dat_csv$Annotation == "drinK"] <- "drink"
dat_csv$Annotation[dat_csv$Annotation == "other chew"] <- "eat_n"


#### subset data ####
meals <- subset(dat_csv, Paradigm == "Meal") # This dateframe excludes drinks
snacks <- subset(dat_csv, Paradigm == "Snack") # This dateframe excludes drinks

```

```{r Calculate variables, include=FALSE}

## TO DO: Manually calculate chew time and meal dur for someone to make sure calculations are correct

## Note: meal time here is calculated from start of first bite, to end of last bite. DRINKS ARE IGNORED
## Note: chew_per_new_bite is the average num of chew/ *new* bite (eat_f annotation) 
## Note: chew_per_bite is the average num of chews/bite, when including all chews between 1 bite and the next

#### For meals ####
# create empty dataframe with 1 row per meal
meals_means <- data.frame(matrix("", nrow = 30))[-1]

ParIDs <- unique(meals$parid)
i = 1
for (ID in ParIDs) {
  subj_meals <- meals[meals$parid==ID,] #subset participant data
  nummeal <- unique(subj_meals$session) #identify number of meals
  for (meal in nummeal) {
    # subset single meal session
    subj_meal <- subj_meals[subj_meals$session==meal,]
    # identify start of first bite
    f <- first(subj_meal$id) ## Note: the meals/subj_meal dataframe does not contain drink events. Using first() instead of id=1 to identify the first bite because if a meal started with a drink, id=1 would not be the first bite (and would not be included in this dataframe))
    mealstart <- strptime((subj_meal$start_time[subj_meal$id==f]), format = "%H:%M:%S")
    # identify end of last bite
    l <- last(subj_meal$id)
    mealend <- strptime((subj_meal$end_time[subj_meal$id==l]), format = "%H:%M:%S")
    # calculate meal duration
    mealdur_min <- mealend-mealstart
    
    # calculate average # of chews per bite (eat_f and eat_n included in chew count); add to database 
    #subj_meal_f <- subset(subj_meal, Annotation == "eat_f")
    number_bites <- length(which(subj_meal$Annotation == "eat_f"))
    chew_per_bite <- sum(subj_meal$chewtimes) / number_bites

    # calculate average # of chews in a "new" bite (eat_f only); add to database 
    subj_meal_f <- subset(subj_meal, Annotation == "eat_f") # creates database with only new bites (eat_f)
    chew_per_new_bite <- mean(subj_meal_f$chewtimes, na.rm=T)
    
    # Add variables to database
    meals_means$parid[i] <- ID
    meals_means$session[i] <- meal
    meals_means$mealdur_min[i] <- mealdur_min
    meals_means$chew_per_bite[i] <- chew_per_bite
    meals_means$chew_per_new_bite[i] <- chew_per_new_bite
    
    i = i + 1
  }
}

snack_means <- data.frame(matrix("", nrow = 30))[-1]

#### repeat for snack paradigm ####
ParIDs <- unique(snacks$parid)
i = 1
for (ID in ParIDs) {
  subj_snacks <- snacks[snacks$parid==ID,] #subset participant data
  nummeal <- unique(subj_snacks$session) #identify number of meals
  for (meal in nummeal) {
    # subset single meal session
    subj_snack <- subj_snacks[subj_snacks$session==meal,]
    # identify start of first bite
    f <- first(subj_snack$id) ## Note: the meals/subj_snack dataframe does not contain drink events. Using first() instead of id=1 to identify the first bite because if a meal started with a drink, id=1 would not be the first bite (and would not be included in this dataframe))
    mealstart <- strptime((subj_snack$start_time[subj_snack$id==f]), format = "%H:%M:%S")
    # identify end of last bite
    l <- last(subj_snack$id)
    mealend <- strptime((subj_snack$end_time[subj_snack$id==l]), format = "%H:%M:%S")
    # calculate meal duration
    mealdur_min <- mealend-mealstart
    
    # calculate average # of chews per bite (eat_f and eat_n included in chew count); add to database 
    #subj_meal_f <- subset(subj_snacks, Annotation == "eat_f")
    number_bites <- length(which(subj_snack$Annotation == "eat_f"))
    chew_per_bite <- sum(subj_snack$chewtimes) / number_bites

    # calculate average # of chews in a "new" bite (eat_f only); add to database 
    subj_snack_f <- subset(subj_snack, Annotation == "eat_f") # creates database with only new bites (eat_f)
    chew_per_new_bite <- mean(subj_snack_f$chewtimes, na.rm=T)
    
    # Add variables to database
    snack_means$parid[i] <- ID
    snack_means$session[i] <- meal
    snack_means$mealdur_min[i] <- mealdur_min
    snack_means$chew_per_bite[i] <- chew_per_bite
    snack_means$chew_per_new_bite[i] <- chew_per_new_bite
    
    i = i + 1
  }
}

```

```{r bar graphs, include=FALSE}
library(ggplot2)

meals_means$session <- as.character(meals_means$session)

snack_means$session <- as.character(snack_means$session)

#### meal duration #### 
ggplot(meals_means, aes(fill=session, y=mealdur_min, x=parid)) + 
    geom_bar(position=position_dodge(preserve = "single"), stat="identity")

ggplot(snack_means, aes(fill=session, y=mealdur_min, x=parid)) + 
    geom_bar(position=position_dodge(preserve = "single"), stat="identity")

#### average chews per bite #### 
ggplot(meals_means, aes(fill=session, y=chew_per_bite, x=parid)) + 
    geom_bar(position=position_dodge(preserve = "single"), stat="identity")


```

```{r descriptives inter-bite-intervals}
library(ggplot2)

### Notes:
# IBI is time between the start of new bites (includes time with food is in mouth). Does not consider that FoodType may effect time in mouth. If using IBI, would need to control for food type
# Inter_eat_f ignores non-bites chewing events. This is not ideal
# Inter_eat_n is the time between the last time food was chewed and new bite

#### Descriptives: IBI ####
psych::describe(meals$IBI, na.rm = TRUE)
psych::describe(snacks$IBI, na.rm = FALSE)

#### Histogram: IBI ####
ggplot(meals,aes(x = IBI)) + geom_histogram(bins = 15) + facet_grid(parid~session)

ggplot(snacks,aes(x = IBI)) + geom_histogram(bins = 15) + facet_grid(parid~session) + scale_x_continuous(limits=c(0, 100))

#### Descriptives: InterEatInt_n ####
psych::describe(meals$InterEatInt_n, na.rm = TRUE)
psych::describe(snacks$InterEatInt_n, na.rm = FALSE)


#### Histogram: InterEatInt_n ####
ggplot(meals,aes(x = InterEatInt_n)) + geom_histogram(bins = 15) + facet_grid(parid~session) + scale_x_continuous(limits=c(0, 60))

ggplot(snacks,aes(x = InterEatInt_n)) + geom_histogram(bins = 15) + facet_grid(parid~session) + scale_x_continuous(limits=c(0, 100))

# histogram with density plot
ggplot(meals, aes(x=InterEatInt_n)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 15) +
  geom_density(alpha=.2, fill="#FF6666") +
  facet_grid(parid~session)+
  scale_x_continuous(limits=c(0, 60))

ggplot(snacks, aes(x=InterEatInt_n)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 30) +
  geom_density(alpha=.2, fill="#FF6666") +
  facet_grid(parid~session)+
  scale_x_continuous(limits=c(0, 750))


#### Timeseries: Inter_eat_n ####
# id is the bite number
ggplot(meals,aes(x=id,y=InterEatInt_n,colour=parid,group=parid)) + geom_line() + facet_grid(parid~session) + scale_y_continuous(limits=c(0, 50))


```

```{r descriptives chew time}

#### Chew Times by parid by visit ####
# only assess # of chews for new bites (category = 0)
ggplot(meals[which(meals$category==0),],aes(x = chewtimes)) + geom_histogram(bins = 15) + facet_grid(parid~session) + scale_x_continuous(limits=c(0, 80))

ggplot(snacks[which(snacks$category==0),],aes(x = chewtimes)) + geom_histogram(bins = 15) + facet_grid(parid~session) + scale_x_continuous(limits=c(0, 80))

```


```{r graph food choice X time}

ggplot(meals, aes(x=id,y=Foodtype, colour=parid,group=parid)) + geom_bar(stat='identity') + facet_grid(parid~session)

```

Can you compare distributions (e.g. the distributions of the IBIs)?
Why? do the distributions differ across meal types? within a person? between people?

Kolmogorov–Smirnov test?
This is because, the K-S statistic quantifies the greatest distance between the empirical distribution functions of two samples and tests if the observed distance is greater than expected.
https://chemicalstatistician.wordpress.com/2013/06/25/exploratory-data-analysis-2-ways-of-plotting-empirical-cumulative-distribution-functions-in-r/ 

```{r compare distributions}
# QUESTION: Do the distributions of IBIs differ between meal types (meal vs. snack)? within a person? between people?
# H1: Distributions of IBIs will differ between meals and snacks
# H2: For the same meal type, distributions of IBIs will be similar (not differ) within a person
# H3: For the same meal type, distributions of IBIs will vary between people, but not as much as between meals vs. snacks

# Kolmogorov–Smirnov test: quantifies the greatest distance between the empirical distribution functions of two samples and tests if the observed distance is greater than expected. The KS test finds the maximum distance between the ECDFs. More importantly, the test requires evaluating whether the distance is large enough to claim that the two samples do not belong to each other.
# https://towardsdatascience.com/how-to-compare-two-distributions-in-practice-8c676904a285

#### snack vs meal overall ####
## Do snack-IBI and meal-IBI come from the same distribution? (H1)
ks.test(meals$IBI, snacks$IBI) #not sure if this is valid bc there are repeated measures within a meal and subject?
ks.test(meals[which(meals$session==1),]$IBI, snacks[which(meals$session==1),]$IBI) #only using session 1 data for each person.

#### D-test statistic matrix ####



```

ICC
To do: statistically examine between and within subject variability

(1) For "between-meal" variables (i.e. 1 value per meal): assess variability between meals for each subject (e.g. variability between meal 1 and meal 2), and variability between subjects

(2) For "within-meal" variables (i.e. repeat values per meal): assess variability across ALL meals for each subject (e.g. ignoring session), and between subjects [is this valid???]

```{r ICC "within meal" variables, ignoring session}
library(lme4)
# ICC is the % of total variability that is between person
# 1-ICC is the % of total variability that is within person


#### Chewtimes ####
# meals
emptymodel <- lmer(formula = chewtimes ~ 1 + (1|parid), 
              data=meals,
              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between #0.1089099

# snacks
emptymodel <- lmer(formula = chewtimes ~ 1 + (1|parid), 
              data=snacks,
              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between #0.08835908

#### IBI ####
# meals
emptymodel <- lmer(formula = IBI ~ 1 + (1|parid), 
              data=meals,
              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between #0.07767203

# snacks
#emptymodel <- lmer(formula = IBI ~ 1 + (1|parid), 
#              data=snacks,
#              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between 


#### InterEatInt_n ####
# meals
emptymodel <- lmer(formula = InterEatInt_n ~ 1 + (1|parid), 
              data=meals,
              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between #0.04215449 ... 4% of the variance is accounted for by between-person differences

# snacks
#emptymodel <- lmer(formula = InterEatInt_f ~ 1 + (1|parid), 
#              data=snacks,
#              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between 
```


```{r ICC "between meal" variables}
library(lme4)

#### chewavg ####
emptymodel <- lmer(formula = chewavg ~ 1 + (1|parid), 
              data=meals_means,
              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between #0.5680399

#### meal duration ####
emptymodel <- lmer(formula = mealdur_min ~ 1 + (1|parid), 
              data=meals_means,
              na.action=na.exclude)
RandomEffects <- as.data.frame(VarCorr(emptymodel))
#ICC = intercept variance / total variance
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between #0.6302614
```

```{r Event in Interval}
library(ggplot2)
library(reshape2)
library(tidyr)
library("Hmisc")
library("corrplot")

setwd(file.path(basedir,"Scripts/"))
source("Event_in_interval.R")

#### BiteCount over time graphs  ####

## Equal size intervals ##

# Meal timeseries number of bites per 60s interval
ggplot(Meal_Event_in_time_interval_60,aes(x=IntNum,y=EventCount,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)

# Snack paradigm timeseries: number of bites per 60s interval
ggplot(Snack_Event_in_time_interval_60,aes(x=IntNum,y=EventCount,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)

# Histogram
ggplot(Meal_Event_in_time_interval_20,aes(x = EventCount)) + geom_histogram() + facet_grid(ParID~session) + scale_x_continuous()
ggplot(Meal_Event_in_time_interval_60,aes(x = EventCount)) + geom_histogram() + facet_grid(ParID~session) + scale_x_continuous()

ggplot(Meal_Event_in_time_interval_30, aes(x=EventCount)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 15) +
  geom_density(alpha=.2, fill="#FF6666") +
  facet_grid(ParID~session)+
  scale_x_continuous()



## Equal number of intervals ##

# Timeseries: number of bites per percentage interval for each meal (30 intervals per meal)
ggplot(Meal_Event_in_percentage_interval_30,aes(x=IntNum,y=EventCount,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)

# Timeseries: number of bites per percentage interval for each meal (20 intervals per meal)
ggplot(Meal_Event_in_percentage_interval_20,aes(x=IntNum,y=EventCount,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)

#Timeseries: number of bites per percentage interval for each meal (5 intervals per meal)
ggplot(Meal_Event_in_percentage_interval_5,aes(x=IntNum,y=EventCount,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)

# Timeseries: number of bites per per percentage interval for each meal (20 intervals per meal)
ggplot(Snack_Event_in_percentage_interval_20,aes(x=IntNum,y=EventCount,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)



#### Graph cumulative variables over time ####
ggplot(Meal_Event_in_percentage_interval_50,aes(x=IntNum,y=EventCount_cumulative,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)
ggplot(Meal_Event_in_percentage_interval_50,aes(x=IntNum,y=EventOccur_cumulative,colour=ParID,group=ParID)) + geom_line() + facet_grid(ParID~session)


#### Correlate bite counts between all meals ####
# Transpose dataset long to wide
Reduced.df <- Meal_Event_in_percentage_interval_50[c("ID","IntNum" ,"EventCount")]
wide <- as.matrix(spread(Reduced.df, ID, EventCount))[,-1]

M<-cor(wide)
corrplot(M, method="circle")

corrmat <-rcorr(wide, type=c("pearson"))
round((corrmat$r),2) # Matrix of correlation coeficients
round((corrmat$P),2) # Matrix of unadjusted p-values

```


```{r Average IEI by within-meal interval}
library(ggplot2)
library(reshape2)
library(tidyr)
library("Hmisc")
library("corrplot")

setwd(file.path(basedir,"Scripts/"))
source("Event_in_interval.R")

#### Average IBI over time  ####

# Timeseries: average IBI per within-meal interval (10 intervals per meal)
#ggplot(Meal_Event_in_percentage_interval_10,aes(x=IntNum,y=IBI_avg,colour=ParID,group=ParID)) + geom_bar(stat = 'identity' ) + facet_grid(ParID~session)

#ggplot(Meal_Event_in_percentage_interval_5,aes(x=IntNum,y=IBI_avg,colour=ParID,group=ParID)) + geom_bar(stat = 'identity' ) + facet_grid(ParID~session)

#ggplot(Meal_Event_in_time_interval_60,aes(x=IntNum,y=IBI_avg,colour=ParID,group=ParID)) + geom_bar(stat = 'identity' ) + facet_grid(ParID~session)

#### Average IEI over time  ####
ggplot(Meal_Event_in_percentage_interval_20,aes(x=IntNum,y=IEI_avg,colour=ParID,group=ParID)) + geom_bar(stat = 'identity' ) + facet_grid(ParID~session)

ggplot(Meal_Event_in_time_interval_20,aes(x=IntNum,y=IEI_avg,colour=ParID,group=ParID)) + geom_bar(stat = 'identity' ) + facet_grid(ParID~session)

ggplot(Meal_Event_in_percentage_interval_10,aes(x=IntNum,y=IEI_avg,colour=ParID,group=ParID)) + geom_bar(stat = 'identity' ) + facet_grid(ParID~session)

ggplot(Meal_Event_in_percentage_interval_5,aes(x=IntNum,y=IEI_avg,colour=ParID,group=ParID)) + geom_bar(stat = 'identity' ) + facet_grid(ParID~session)


```
